\documentclass[journal,12pt,twocolumn]{IEEEtran}
%
\usepackage{setspace}
\usepackage{gensymb}
\usepackage{xcolor}
\usepackage{caption}
%\usepackage{subcaption}
%\doublespacing
\singlespacing

%\usepackage{graphicx}
%\usepackage{amssymb}
%\usepackage{relsize}
\usepackage[cmex10]{amsmath}
\usepackage{mathtools}
%\usepackage{amsthm}
%\interdisplaylinepenalty=2500
%\savesymbol{iint}
%\usepackage{txfonts}
%\restoresymbol{TXF}{iint}
%\usepackage{wasysym}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{txfonts}
\usepackage{stfloats}
\usepackage{cite}
\usepackage{cases}
\usepackage{subfig}
%\usepackage{xtab}
\usepackage{longtable}
\usepackage{multirow}
%\usepackage{algorithm}
%\usepackage{algpseudocode}
%\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{mathtools}
%\usepackage{iithtlc}
%\usepackage[framemethod=tikz]{mdframed}
\usepackage{listings}
\usepackage{scalerel}
\usepackage{stackengine}
\usepackage{xcolor}
\newcommand\showdiv[1]{\overline{\smash{\hstretch{.5}{)}\mkern-3.2mu\hstretch{.5}{)}}#1}}
\usepackage{polynom}
%\usepackage{stmaryrd}


%\usepackage{wasysym}
%\newcounter{MYtempeqncnt}
\DeclareMathOperator*{\Res}{Res}
%\renewcommand{\baselinestretch}{2}
\renewcommand\thesection{\arabic{section}}
\renewcommand\thesubsection{\thesection.\arabic{subsection}}
\renewcommand\thesubsubsection{\thesubsection.\arabic{subsubsection}}

\renewcommand\thesectiondis{\arabic{section}}
\renewcommand\thesubsectiondis{\thesectiondis.\arabic{subsection}}
\renewcommand\thesubsubsectiondis{\thesubsectiondis.\arabic{subsubsection}}

%\renewcommand{\labelenumi}{\textbf{\theenumi}}
%\renewcommand{\theenumi}{P.\arabic{enumi}}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\lstset{
	language=Python,
	frame=single, 
	breaklines=true,
	columns=fullflexible
}


\begin{document}

TASK 3b 4 plan

Events $\equiv$ Ice-cube \quad Source $\equiv$ ms Psr

LUO\& ZHANG - $2004.09686$

\begin{enumerate}

\item  Select $v$ events $\geqslant 100$ TeV

$$
\Rightarrow \log _{10} E / GeV \geqslant 5
$$

Pulsar

\item . Select $D$ events with $\angle^{le}$ to interesfed source $<20^{\circ}$

\item  $B i=$ # events in dataset with solid $\angle^{\text {le }}$ arerage across a band of $\pm 6^{\circ}$ in the declination around the source Solid L'

\item  $S_{i}=\frac{1}{2 \pi \sigma_{i}}=\exp \left(-\frac{\left|\bar{x}-\bar{x}_{s}\right|^{2}}{2 \sigma_{i}^{2}}\right)$

$\sigma_{i}$ is uncertoinity associated with each event $\sigma_{i}=A_{\text {ingers of }} i^{\text {M }} v_{\text {-event in }}$ ) $C$ data

\item  Estimate the B.G PDF by calculating Hevents per-steradion

Total # events

$\left|\bar{x}_{i}-\bar{x}_{b}\right|^{2}=$ spoce le b/w $^{\text {th }} \vee \& s^{\text {in }}$ msp 5. For a total $N$ events:

PDF for $i^{\text {th }}$ event $\equiv p[i]=\frac{n_{s}}{N} S_{i}+\left(1-\frac{n_{s}}{N}\right) B_{i}$ $n_{s}=$ # events accredited to the source

$\longrightarrow$ ??

\item  Likelihood Pu of entire dataset $=\mathcal{L}\left(n_{s}\right)$

$$
\mathcal{L}\left[n_{s}\right]=\prod_{i=1}^{N} \frac{n_{s}}{N} S_{i}+\left(1-\frac{n_{s}}{N}\right) B_{i}
$$

$n_{s}$ is determined by maximizing $\mathcal{L}$

\item  Define a test statistic


$$
T S=2 \frac{\ln \mathcal{L}\left(\tilde{n s}_{s}\right)}{\ln \mathcal{L}(0)}
$$

Equivalent to the ratio of 2 Hypotheses $H_{1}=O f$ all the $N$ events, $n_{s}$ are produced by the interested soorce $H_{0}=$
\end{enumerate}

All the Nevents are Bockground Events.\\

The likelihood ratio will indicate how likely is that some of the $v$ - events can be attributed to the source we are trying to test the association with different $v$-flux background PDF ( $\left.B_{i}\right)$

Avg now events per steradian - At Each Sedination Total # Events

Paper uses events which hove a high Probabilities of being Cosmic.

Likel, hood ratio obterined $\square$

Relative measurement of how /ikely to reject Null hypothes

NuLL HyPotHEsis: ALL the observed $v$-events around the interested source are NOT produced
by that source

$F_{\text {ails }}$ to indicate the level of significance $\rightarrow$ of what 1

Improperly defines the contributions of $n_{5}$ (fitted # source events) to the association of $v$-events.

$\rightarrow$ i.e Diffinult to say which has stronger association.

Source with

Source with

more filted Source events Less fitted source events

lower likelihood ratio higher likelihood ratio. $\therefore$ For Each source with $n_{s}$, TS $>0$ Monte Carlo Simulation

Randomly generate $v$ events isotropically distributed around the interested source within $20^{\circ}$ distance.

$\downarrow$

Assign E to all gen events using

Kernel density Estimation of the Observed $\nu$ Energy-Dist. of each year.

I $\rightarrow$ from the relationshipof Obs.Even" $E$ Localization Error: $f_{n}$ (simulated $E$, AngExr in ICDAPA) 1 Some Event selection Distribution of $n_{s}$, TS.

Linfer significance by $L$ In the pupper, i11ler to Normol Dist. Compore with Observed result \& find $\frac{p \text {-value }}{L}$ \%tile observed values lie in
\end{document}